Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Caption
Sliiiightly more space

        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$t_{1}$};

@@

        \path (p) edge (a) edge (c)
            (a) edge (d)
            (c) edge (d);
    \end{tikzpicture}
    \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
    \label{fig:klessexample}
\end{figure}
\end{example}

>>>>

        \node[draw=none,right of = b3,node distance=1mm, yshift=-2.5mm] {$t_{1}$};

@@

        \path (p) edge (a) edge (c)
            (a) edge (d)
            (c) edge (d);
    \end{tikzpicture}
    \caption{There is a non-induced isomorphism $P\rightarrowtail T_{1}$ from the first graph to the
    second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
    is a $1$-less isomorphism $P\lessnonind{1} T_{2}$ omitting vertex $b$.}\label{fig:klessexample}
\end{figure}
\end{example}
